%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Satyam Tomar} \\ \vspace{1pt}
    Haripur Kalan, Dehradun, Uttarakhand, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 8077571779 ~ \href{mailto:satyam321tomar@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{satyam321tomar@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/satyam-stellar/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/satyam-stellar}}  ~
    \href{https://satyamstellar.space/}{\raisebox{-0.2\height}\faLink\ \underline{satyamstellar.space}}
    \vspace{-5pt}
\end{center}

\section{Summary}
A tech enthusiast with 3+ years of hands-on experience in web development, specializing in modern JavaScript frameworks like React and UI/UX design. Adept at problem solving and quickly adaptable, driven by curiosity and a passion for crafting innovative digital solutions.

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
\noindent
\textbf{• Web Development} \hfill \textbf{• Database Management} \hfill \textbf{• Computer Networks} \hfill \textbf{• Operating Systems}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: JavaScript, Python, SQL, C, C++} \\
\textbf{Libraries/Frameworks}{: React, Tailwind CSS, GSAP, Node.js, Express.js, Prisma,Zod, Django} \\
\textbf{Databases}{: Firebase, MongoDB, PostgreSQL} \\
\textbf{Cloud \& DevOps}{: GitHub Action,  Vercel, Render, AWS(Basic), Azure(Basic) }\\
\textbf{Tools/Other}{: Git, VSCode, Neovim, Ubuntu, Arch Linux, Networking }
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {DMarketingGuru (Digital Marketing Agency)}{Jan 2024 -- Mar 2024}
    {Video Editor \& Social Media Assistant}{Dehradun, Uttarakhand}
    \resumeItemListStart
      \resumeItem{Managed and edited content for the official Instagram account, boosting engagement and follower growth.}
      \resumeItem{Edited promotional and educational videos using industry-standard tools.}
      \resumeItem{Wrote scripts and created copy for various campaigns and social media reels.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Real-Life Agency Website} $|$ \emph{React, Vite, Tailwind CSS, GSAP, Framer Motion}}{}
    \resumeItemListStart
      \resumeItem{Developed a performant, SEO-optimized agency website with a modern and responsive UI.}
      \resumeItem{Integrated scroll-based animations and interactive UI elements using GSAP and Framer Motion.}
      \resumeItem{Used component-driven architecture with Tailwind’s utility classes for scalable development.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Gmail Clone} $|$ \emph{React, Vite, Tailwind CSS, Firebase, Redux, Framer Motion}}{}
    \resumeItemListStart
      \resumeItem{Engineered a Gmail-inspired app with inbox, compose, and email detail views.}
      \resumeItem{Enabled user authentication and real-time data sync via Firebase Firestore.}
      \resumeItem{Implemented Redux Toolkit for robust global state management.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Trello Clone} $|$ \emph{React, Vite, Tailwind CSS, react-beautiful-dnd}}{}
    \resumeItemListStart
      \resumeItem{Developed a Trello-inspired task management app with responsive design using React and Vite.}
      \resumeItem{Implemented drag-and-drop functionality with the `react-beautiful-dnd` library for task management.}
      \resumeItem{Crafted reusable components for lists, cards, and task management with dynamic updates.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Booksy} $|$ \emph{React, Vite, Tailwind CSS, Node.js, Express, PostgreSQL, Prisma, Vercel}}{}
    \resumeItemListStart
      \resumeItem{Developed a full-stack CRUD application to manage books with create, update, delete, and search features.}
      \resumeItem{Crafted a responsive UI with modals, alerts, and reusable components.}
      \resumeItem{Built RESTfull APIs using Express and PostgreSQL, abstracted with Prisma ORM.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {HEC Group of Institutions}{Haridwar, Uttarakhand}
      {Bachelor of Computer Applications }{}
\resumeSubHeadingListEnd

\end{document}
